Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-02-23 bw-prop.tex
adds BDBA concept
Change JFNK to Newton-Krylov since that incorporates both traditional and matrix-free methods.

\paragraph{Role of Blue Waters}
Simulations which faithfully capture this coupling at realistic spatial and
temporal resolution are only possible with the aid of high performance
computing resources.  To solve these large systems of partial differential
equations on a finite element mesh in a fully-coupled, implicit way, the MOOSE
framework was designed to take advantage of high performance computing
capability.  The framework conducts fully implicit physics coupling with a
Jacobian Free Newton Krylov (JFNK) solver method and sophisticated automatic
adaptive meshing.  These simulations are memory intensive, so the exceptional
memory capability of the Blue Waters resource will be essential to performant
simulation times. It is also important to note that rendering visualizations of
the results can be computationally intensive was well.

@@

Initial simulations of the MSRE have been conducted both locally on the desktop 
computer scale and on Blue Wates. These have been steady state simulations and 
have occupied up to many hundreds of nodes simultaneously. This talk will 
describe how coupling between neutronics and thermal hydraulics ahve been 
established in the Moltres tool as well as the validation and verification 
efforts which are ongoing.

In the near term, these steady state calculations will provide the initial 
conditions for full core reactor transient simulations. Such simulations 
commonly occupy tens of thousands of CPU cores at a time and vary in completion 
time. The MOOSE framework is shown to scale very well up to 10,000 cores. 
Transient and multi-scale simulations, which require greater capability per 
simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those 
larger simulations are likely to be run this year..

>>>>

\paragraph{Role of Blue Waters}
Simulations which faithfully capture this coupling at realistic spatial and
temporal resolution are only possible with the aid of high performance
computing resources.  To solve these large systems of partial differential
equations on a finite element mesh in a fully-coupled, implicit way, the MOOSE
framework was designed to take advantage of high performance computing
capability.  The framework conducts fully implicit physics coupling with
Newton-Krylov based solver methods and sophisticated automatic
adaptive meshing.  These simulations are memory intensive, so the exceptional
memory capability of the Blue Waters resource will be essential to performant
simulation times. It is also important to note that rendering visualizations of
the results can be computationally intensive was well.

@@

Initial simulations of the MSRE have been conducted both locally on the desktop
computer scale and on Blue Wates. These have been steady state simulations and
have occupied up to many hundreds of nodes simultaneously. This talk will
describe how coupling between neutronics and thermal hydraulics have been
established in the Moltres tool as well as the validation and verification
efforts which are ongoing.

In the near term, these steady state calculations will provide the initial
conditions for full core reactor transient simulations. Such simulations
commonly occupy tens of thousands of CPU cores at a time and vary in completion
time. The MOOSE framework is shown to scale very well up to 10,000 cores.
Transient and multi-scale simulations, which require greater capability per
simulation, may occupy up to 100,000 CPU cores at a time. Such transient
simulations will evaluate the safety performance of advanced reactors in severe
(beyond design basis) accidents.
